Analysis of HTTPS Adoption and Third-party Tracking: \\A Swedish Perspective

### 2015-04-29 paper/figures.tex
Draft scatter plot over http/https disconnect categories

>>>>

\begin{tikzpicture}
\begin{groupplot}[
	group style={
		group size=2 by 1,
		horizontal sep=8pt,
		vertical sep=16pt,
	},
]

	\nextgroupplot[
		title=C1 Sweden,
		xlabel=http-www,
		ylabel=https-www,
		allDatasetsScatter,
		allDatasetsScatterMiniResults,
		scatter/classes={
			Any={mark=square*,blue},%
			Disconnect={mark=triangle*,red},%
			Content={mark=x,draw=black},%
			Advertising={mark=o,draw=red},%
			Analytics={mark=diamond,draw=blue},%
			Social={mark=+,draw=green}%
		},%
	]
	\addDefaultScatterTableDatasetsNonFailedDisconnectCategoriesCoverageExternalSortedSwedenHttpHttpsWww

	\nextgroupplot[
		title=C2 Global,
		xlabel=http-www,
		% ylabel=https-www,
		allDatasetsScatter,
		allDatasetsScatterMiniResults,
		scatter/classes={
			Any={mark=square*,blue},%
			Disconnect={mark=triangle*,red},%
			Content={mark=x,draw=black},%
			Advertising={mark=o,draw=red},%
			Analytics={mark=diamond,draw=blue},%
			Social={mark=+,draw=green}%
		},%
		yticklabels={},
	]
	\addDefaultScatterTableDatasetsNonFailedDisconnectCategoriesCoverageExternalSortedGlobalHttpHttpsWww

### 2015-04-29 paper/tableread.tex
Draft scatter plot over http/https disconnect categories

>>>>

%%% Create tables on the fly

\newcommand{\scatterTableDatasetsNonFailedDisconnectCategoriesCoverageExternalSortedHttpHttpsWww}[4]{
	\pgfplotstableset{
		create on use/Dataset/.style={create col/copy column from table={#3}{Dataset}},%
		create on use/Category/.style={create col/set={#1}},%
		create on use/http-www/.style={create col/copy column from table={#3}{#1}},%
		create on use/https-www/.style={create col/copy column from table={#4}{#1}},%
	}

	\pgfplotstablenew[
		columns={
			Dataset,%
			Category,%
			http-www,%
			https-www%
		}
	]{\pgfplotstablegetrowsof{#3}}#2%
}
